Untitled

### 2025-03-20 script/r/draft.Rmd
maj inst: ok pour democ, à creuser pour medias
Media freedom and democracy indexes

data_final%<>%
  mutate(desert_region_tv=desert_region*tv,
         mountain_region_tv=mountain_region*tv)

@@

>>>>

data_final%<>%
  mutate(desert_region_tv=desert_region*tv,
         mountain_region_tv=mountain_region*tv,
         elevation_region_tv=elevation_region*tv)

@@

```{r}
vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")

vdem%<>%
  select(country_text_id, year, v2xedvd_inpt, v2x_polyarchy, v2xedvd_me_cent, v2medstateprint, v2medstatebroad, v2medpolstate, v2medpolnonstate, e_v2x_freexp_altinf_3C, e_v2x_freexp_altinf_4C, e_v2x_freexp_altinf_5C, v2x_freexp, v2xme_altinf, e_polity2)

vdem%<>%
  filter(country_text_id %in% countries)

vdem%<>%
  rename(iso=country_text_id)%>%
    mutate(round=case_when(between(year, 2011, 2013)~5,
                         between(year, 2014, 2015)~6,
                         between(year, 2016, 2018)~7,
                         between(year, 2019, 2021)~8,
         TRUE~NA_integer_))

vdem %<>%
  group_by(iso, round) %>%
  filter(!is.na(round)) %>%
  mutate(
    v2xedvd_inpt_mean2 = ifelse(all(is.na(v2xedvd_inpt)), NA_integer_, mean(v2xedvd_inpt, na.rm = TRUE)),
    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
    v2xedvd_me_cent_mean2 = ifelse(all(is.na(v2xedvd_me_cent)), NA_integer_, mean(v2xedvd_me_cent, na.rm = TRUE)),
    v2medstateprint_mean2 = ifelse(all(is.na(v2medstateprint)), NA_integer_, mean(v2medstateprint, na.rm = TRUE)),
    v2medstatebroad_mean2 = ifelse(all(is.na(v2medstatebroad)), NA_integer_, mean(v2medstatebroad, na.rm = TRUE)),
    v2medpolstate_mean2 = ifelse(all(is.na(v2medpolstate)), NA_integer_, mean(v2medpolstate, na.rm = TRUE)),
    v2medpolnonstate_mean2 = ifelse(all(is.na(v2medpolnonstate)), NA_integer_, mean(v2medpolnonstate, na.rm = TRUE)),
    e_v2x_freexp_altinf_3C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_3C)), NA_integer_, mean(e_v2x_freexp_altinf_3C, na.rm = TRUE)),
    e_v2x_freexp_altinf_4C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_4C)), NA_integer_, mean(e_v2x_freexp_altinf_4C, na.rm = TRUE)),
    e_v2x_freexp_altinf_5C_mean2 = ifelse(all(is.na(e_v2x_freexp_altinf_5C)), NA_integer_, mean(e_v2x_freexp_altinf_5C, na.rm = TRUE)),
    v2x_freexp_mean2 = ifelse(all(is.na(v2x_freexp)), NA_integer_, mean(v2x_freexp, na.rm = TRUE)),
    v2xme_altinf_mean2 = ifelse(all(is.na(v2xme_altinf)), NA_integer_, mean(v2xme_altinf, na.rm = TRUE)),
    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
  ) %>%
  ungroup()

vdem%<>%
  mutate(e_polity2_med_all=ifelse(is.na(round), NA_integer_, median(e_polity2, na.rm=TRUE)))

vdem%<>%
  select(iso, round, v2xedvd_inpt_mean2, v2x_polyarchy_mean2, v2xedvd_me_cent_mean2, v2medstateprint_mean2, v2medstatebroad_mean2, v2medpolstate_mean2, v2medpolnonstate_mean2, e_v2x_freexp_altinf_3C_mean2, e_v2x_freexp_altinf_4C_mean2, e_v2x_freexp_altinf_5C_mean2, v2x_freexp_mean2, v2xme_altinf_mean2, e_polity2_mean2, e_polity2_med_all)%>%
    distinct(iso, round, .keep_all = TRUE)

data_final %<>% left_join(vdem, by=c("iso", "round"))

### 2025-03-20 script/r/rbci_data.Rmd
Media freedom and democracy indexes

```{r}
#MAJ VDEM

@@

countries <- unique(data_final$iso)

qog%<>%
  mutate(round=case_when(between(year, 2011, 2013)~5,
                         between(year, 2014, 2015)~6,
                         between(year, 2016, 2018)~7,
                         between(year, 2019, 2021)~8,
         TRUE~NA_integer_))

qog%<>%
  group_by(iso, round)%>%
  mutate(poly_mean = ifelse(is.na(round), NA_integer_, mean(vdem_polyarchy, na.rm = TRUE))) %>%
  mutate(med_corr_mean = ifelse(is.na(round), NA_integer_, mean(vdem_med_corrupt, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  select(iso, round, poly_mean, med_corr_mean)

data_final %<>% left_join(qog, by=c("iso", "round"))

saveRDS(data_final, file="data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")
```

>>>>

```{r}
#Media freedom and democracy indexes

@@

countries <- data_final %>% filter(spl == 1) %>% pull(iso) %>% unique()

qog %<>%
  select(year, ccodealp, rsf_pfi1321, ) %>%
  rename(iso = ccodealp, rsf_index = rsf_pfi1321)

qog %<>%
  mutate(round = case_when(
    year == 2013 ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

qog %<>%
  group_by(iso, round) %>%
  mutate(rsf_index_mean = ifelse(is.na(rsf_index), NA_integer_, mean(rsf_index, na.rm = TRUE))) %>%
  ungroup()

qog %<>%
  filter(!is.na(round)) %>%
  distinct(iso, round, .keep_all = TRUE) %>%
  filter(iso %in% countries) %>%
  mutate(rsf_index_med_all = ifelse(is.na(round), NA_integer_, median(rsf_index_mean, na.rm =
                                                                        TRUE)))
qog %<>%
  select(iso,
         round,
         rsf_index_mean)

data_final %<>% left_join(qog, by = c("iso", "round"))

saveRDS(data_final, file = "data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")

vdem <- readRDS("data/data_raw/V-Dem-CY-Full+Others-v13.rds")

vdem %<>%
  select(country_text_id, year, v2x_polyarchy, e_polity2)

vdem %<>%
  filter(country_text_id %in% countries)

vdem %<>%
  rename(iso = country_text_id) %>%
  mutate(round = case_when(
    between(year, 2011, 2013) ~ 5,
    between(year, 2014, 2015) ~ 6,
    between(year, 2016, 2018) ~ 7,
    between(year, 2019, 2021) ~ 8,
    TRUE ~ NA_integer_
  ))

vdem %<>%
  group_by(iso, round) %>%
  filter(!is.na(round)) %>%
  mutate(
    v2x_polyarchy_mean2 = ifelse(all(is.na(v2x_polyarchy)), NA_integer_, mean(v2x_polyarchy, na.rm = TRUE)),
    e_polity2_mean2 = ifelse(all(is.na(e_polity2)), NA_integer_, mean(e_polity2, na.rm = TRUE))
  ) %>%
  ungroup()

vdem %<>%
  select(iso, round, v2x_polyarchy_mean2, e_polity2_mean2) %>%
  distinct(iso, round, .keep_all = TRUE)

data_final %<>% left_join(vdem, by = c("iso", "round"))

saveRDS(data_final, file = "data/data_rds/data_final.rds")

write_dta(data_final, "data/data_dta/data_final.dta")
